---
title: "Introduction to the function of R and Rcpp"
author: "22001"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the R and Rcpp function of StatComp22001}'
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp22001__ is a simple R package developed to calculate the positive-mean and risk measure. Two functions are considered, namely, _positive.mean_ (calculate the positive parts mean) and _RM_ (calcilate the risk measure of the loss data).  And _gibbsC_ for C++.



## positive mean

The definition of positive mean is $E(X-d)_{+}$,where d in the actuary calls deductible.

The source R code for _positive.mean_ is as follows:
```{r,eval=FALSE}
function(X,d){
  n=length(X)
  a=numeric(n)
  for (i in 1:n) {
    if(X[i]-d>=0)
      a[i]=X[i]-d
    else
      a[i]=0
  }
  return(mean(a))
}
```

The above code shows above can calculate the positive mean when you are given a deductible d and it could be used to calculate the positive part of x-d's mean.

##Risk measure
Some definition of the risk measure:

***Value-at-Risk (VaR)***
$$
\operatorname{VaR}_\alpha(X)=\inf \{x \in \mathbb{R} \mid F(x) \geq \alpha\}, \quad \alpha \in(0,1]
$$
***Conditional VaR (CVaR)***
$$
\operatorname{CVaR}_\alpha(X)=\frac{1}{1-\alpha} \int_\alpha^1 \operatorname{VaR}_u(X) \mathrm{du} .
$$

***Distortion risk measure***


$$
\rho_h(X)=\int_0^1 F^{-1}(\alpha) \operatorname{dh}(\alpha)
$$
Where $h:[0,1] \rightarrow[0,1]$ satisfies $h$ increasing and convex, and $h(0)=h(0+)=0, h(1)=h(1-)=1$. 

***Shortfall risk measure***

$$
S R_{l, \lambda}^P(Z):=\inf _{t \in \mathbb{R}}\left\{t: \mathbb{E}_P[l(-Z-t)] \leq \lambda\right\}
$$

The source R code for _RM_ is as follows:

```{r,eval=FALSE}
function(X,alpha,measure=c('VaR','CVaR','Distortion','Shortfall'),lambda){
  if(measure=='VaR')
  {VaR<-unname(quantile(X,1-alpha))
  return(abs(VaR))
  }
  if(measure=='CVaR')
  {f=function(x)
    x+1/(1-alpha)*positive.mean(X,x)
  CVaR=optimize(f,lower = quantile(X,1-alpha),upper = max(X))
  return(CVaR$objective)
  }
  if(measure=='Distortion')
  {
    f=function(x)
      quantile(X,1-x)*3*x^2
    D=integrate(f,0,1)$value
    return(abs(D))
  }
  if(measure=='Shortfall')
  {
    f=function(x)
      mean(-exp(-(X+x))>=-lambda)
    S=optimize(f,lower = 0,upper = max(X))
    return(S$objective)
  }
}
```

It could be used to calculate the loss of risk measure,such as VaR,CVaR,Distortion and Shortfall.It can be noted that this function has used 'quantile' ,'optimize' function to quantify the loss risk.

The example shows as follows:

```{r,eval=TRUE}
library(StatComp22001)
set.seed(1234)
X<-rnorm(100,0,4)
RM(X,0.9,measure='VaR')
RM(X,0.9,measure='CVaR')
RM(X,measure='Distortion')
RM(X,measure='Shortfall',lambda=20)
```




##  _gibbsC_

 The C++ code is as follows.

```{r,eval=FALSE}
NumericMatrix gibbsC(int N, int thin) {
  NumericMatrix mat(N, 2);
  double x = 0, y = 0;
  for(int i = 0; i < N; i++) {
    for(int j = 0; j < thin; j++) {
      x = rgamma(1, 3, 1 / (y * y + 4))[0];
      y = rnorm(1, 1 / (x + 1), 1 / sqrt(2 * (x + 1)))[0];
    }
    mat(i, 0) = x;
    mat(i, 1) = y;
  }
  return(mat);
}
```

It's the homework from the course of 'statistic computation',which can be used to generate the sample by Gibbs method.
